Efficient pedigree recording for fast population genetics simulation

### 2018-01-10 forwards_paper.tex
Edits from jk

We implemented simulations in a Python script, usable as a command-line utility,
taking input parameters for population size $N$ and scaled recombination $\rho$.
As described in 'Simulation benchmarks', we set scaled mutation $\theta=\rho$,
we used simplify interval of 1000 and simulated for $T=10N$ generations in each
simulation, introducing deleterious mutations at a rate of $\rho/100$ per
generation.
Because \simupop{} requires explicit locations for loci, we set the number of
loci $n=\rho / (4Nr)$ and marked
$k={\rm round}(\mu / (100 (\mu + \mu / 100))) = 0$ of these as selected loci.
\jda{unfortunately probably what we did...}
The selected loci were chosen as a random sample of all the loci.

We coupled \simupop{} to \msprime{} using a Python class \texttt{RecombCollector} 1)
tracks time, and 2) collects and parses recombination information provided by
the \texttt{Recombinator} class of \simupop{}, adding them to a \tnodetable{} and
\tedgetable{} upon which simplification is performed every 1000 years (using
\texttt{msprime.sort\_tables()} and \texttt{msprime.simplify\_tables}).
The tables are initialized using the \texttt{TreeSequence} returned from
\texttt{msprime.simulate($2N$, Ne=$N$, recombination\_rate=$r/2$, length=$n$)}.
The \texttt{simuPOP.Population()} is initialized and tagged with individual IDs,
a mapping of these IDs to the \tnodetable{} IDs is passed to
an instance of \texttt{RecombCollector} and used internally to update the tables.
The \texttt{simuPOP.Population()} is then evolved.
Before mating: selected mutations are created (using
\texttt{simuPOP.SNPMutator}) and multiplicative selection occurs (using
\texttt{simuPOP.PyMlSelector}) only on the selected loci;
the internal time of the \texttt{RecombCollector} instance is updated.
During mating: male and female parents are drawn randomly, recombination data is
output by \simupop{} to the \texttt{RecombCollector} instance.
After mating: nothing happens 999/1000 years, every 1000 years the tables are
simplifed.

>>>>

We implemented simulations in a Python script, usable as a command-line utility,
taking input parameters for population size $N$ and scaled recombination rate $\rho$.
As described in 'Simulation benchmarks', we set scaled mutation rate $\theta=\rho$,
we used simplify interval of 1000 and simulated for $T=10N$ generations in each
simulation, introducing deleterious mutations at a rate of $\rho/100$ per
generation.
Because \simupop{} requires explicit locations for loci, we set the number of
loci $n=\rho / (4Nr)$ and marked
$k={\rm round}(\mu / (100 (\mu + \mu / 100))) = 0$ of these as selected loci.
\jda{unfortunately probably what we did...}
The selected loci were chosen as a random sample of all the loci.

We coupled \simupop{} to \msprime{} using a Python class \texttt{RecombCollector} that 1)
tracks time, and 2) collects and parses recombination information provided by
the \texttt{Recombinator} class of \simupop{}, adding them to a \tnodetable{} and
\tedgetable{} upon which simplification is performed every 1000 generations (using
\texttt{msprime.sort\_tables()} and \texttt{msprime.simplify\_tables}).
The tables are initialized using the \texttt{TreeSequence} returned from
\texttt{msprime.simulate($2N$, Ne=$N$, recombination\_rate=$r/2$, length=$n$)}.
The \texttt{simuPOP.Population()} is initialized and tagged with individual IDs,
a mapping of these IDs to the \tnodetable{} IDs is passed to
an instance of \texttt{RecombCollector} and used internally to update the tables.
The \texttt{simuPOP.Population()} is then evolved.
Before mating: selected mutations are created (using
\texttt{simuPOP.SNPMutator}) and multiplicative selection occurs (using
\texttt{simuPOP.PyMlSelector}) only on the selected loci;
the internal time of the \texttt{RecombCollector} instance is updated.
During mating: male and female parents are drawn randomly, recombination data is
output by \simupop{} to the \texttt{RecombCollector} instance.
After mating: nothing happens 999/1000 generations, every 1000 generations the tables are
simplifed.
